What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java?

### 2015-02-14 android-stacks.tex
Small textual changes to the abstract.
Latex quotes are ``...''

This paper reports a study which mined the exception stack traces included in
159,048 issues reported on Android projects hosted in GitHub (482 projects) 
and Google Code (157 projsects). The goal of this study is to investigate 
whether the analysis of stack trace information could reveal \emph{bug hazards} related to the exception handling code,
 that may lead to a decrease in application robustness. 
 Overall 6,005 exception stack traces were extracted, and analyzed in 
combination with source code and bytecode analysis. 
Some of the outcomes of this study include the identification of the following 
\emph{bug hazards}: (i) unexpected cross-type exception wrappings (for instance, trying to handle an instance 
of OutOfMemoryError ``hidden" in  a checked exception)  which can make the exception-related code 
more complex and negatively impact the application robustness; (ii) undocumented runtime exceptions 
thrown by both the Android platform and third party libraries; and (iii) undocumented checked exceptions
 thrown by the Android Platform. Such undocumented exceptions make difficult, and most of the times infeasible
for the client code to protect against `unforeseen" situations that may happen while calling a third-party code.
This study provides further insights on such \emph{bug hazards} and the robustness threats  
they impose not only to Android apps but also to other systems based on Java exception model.

>>>>

This paper reports on a study mining the exception stack traces included in
159,048 issues reported on Android projects hosted in GitHub (482 projects) 
and Google Code (157 projects). The goal of this study is to investigate 
whether stack trace information can reveal \emph{bug hazards} related to exception handling code that may lead to a decrease in application robustness. 
 Overall 6,005 exception stack traces were extracted, and subjected to source code and bytecode analysis. 
The outcomes of this study include the identification of the following 
\emph{bug hazards}: (i) unexpected cross-type exception wrappings (for instance, trying to handle an instance 
of OutOfMemoryError ``hidden'' in  a checked exception)  which can make the exception-related code 
more complex and negatively impact the application robustness; (ii) undocumented runtime exceptions 
thrown by both the Android platform and third party libraries; and (iii) undocumented checked exceptions
 thrown by the Android Platform. Such undocumented exceptions make difficult, and most of the times infeasible
for the client code to protect against ``unforeseen'' situations that may happen while calling third-party code.
This study provides further insights on such \emph{bug hazards} and the robustness threats  
they impose to Android apps as well as to other systems based on the Java exception model.
